Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-11-25 papers/EMNLP2019/relwork.tex
some changes towards the LREC submission

The purely taxonomic view has been criticized in more recent work on concept organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}. 

>>>>

The purely taxonomic view has been criticized in more recent work on concept organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food, where }. 
